% report template from https://www.overleaf.com/latex/templates/university-of-warwick-es327-cs351-report-template/nndyfbkvfvtm
% and edits inspied by Edmund Goodman (https://github.com/EdmundGoodman/CS310-dissertation/blob/c9b2168154004e7c7f15549ca1d02e1c2b0dff7d/dissertation.tex)

\documentclass[a4paper]{report}

\usepackage[margin=1in]{geometry}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{changepage}
\usepackage{chngcntr}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{graphicx}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{subcaption}

\usepackage{algorithm}
\usepackage{algpseudocode}
\counterwithin{algorithm}{chapter}
\renewcommand{\thealgorithm}{\thechapter.\arabic{algorithm}}

\usepackage{tikz} % fancy diagrams
\usetikzlibrary{positioning,calc}

\usepackage[
    style=numeric,
    maxbibnames=3 % include max 3 names in bib
]{biblatex}
\renewbibmacro{in:}{} % remove "in" so that not hanging if journal name missing
\DeclareNameAlias{default}{family-given} % order names in lastname-firstname
\addbibresource{bibliography.bib}
     
%%%%%%%%%%%%%%%%%%%%

\setlength{\parindent}{0mm}
\setlength{\parskip}{\medskipamount}
\renewcommand\baselinestretch{1.2}

\cleanlookdateon

\makeatletter
\newcommand{\@assignment}[0]{Assignment}
\newcommand{\assignment}[1]{\renewcommand{\@assignment}{#1}}
\newcommand{\@supervisor}[0]{}
\newcommand{\supervisor}[1]{\renewcommand{\@supervisor}{#1}}
\newcommand{\@yearofstudy}[0]{}
\newcommand{\yearofstudy}[1]{\renewcommand{\@yearofstudy}{#1}}
\makeatletter

\author{Joel Coulon}
\title{Evaluating the Resiliency of Blink-Based DeepFake Detection Against Adversarial Noise Attacks}
\supervisor{Long Tran-Thanh}
\yearofstudy{3\textsuperscript{rd} (2024-2025)}

%%%%%%%%%%%%%%%%%%%%

\pagestyle{plain}
% \renewcommand{\headrulewidth}{0.0pt}

\fancypagestyle{plain}{
	\fancyhf{}
	\fancyhead[R]{\textit{Joel Coulon}}
	\fancyhead[L]{\textit{Evaluating the Resiliency of Blink-Based\\DeepFake Detection Against Adversarial Noise Attacks}}
    \fancyfoot[C]{\thepage}
}

%%%%%%%%%%%%%%%%%%%%

\begin{document}

%TC:ignore
\input{dissertation/titlepage}

\pagestyle{plain}

\pagenumbering{gobble}
\begin{abstract}
DeepFakes are pieces of media that have been generated or manipulated by Artificial Intelligence. They can produce realistic videos of humans that are nearly impossible to detect as fake. Hence, the can be used to easily spread misinformation. Convolutional Neural Networks have traditionally been used to reliably detect DeepFake videos. However, these have been shown to be vulnerable to adversarial noise; targeted noise, which is imperceptible to humans, that can be added to an image which causes a previously reliable detector to classify a fake image as real.

Blink-based detectors involve tracking a human's psychological eye blinking patterns to determine if a video has been DeepFaked video. DeepFakes will often blink at a rate that is unnatural and thus can be detected reliably.

This project introduces a novel method of blink detection using univariate time-series analysis on an individual's eyes blinking pattern over the course of a video. It goes on to show that such a method of detection is resilient against adversarial noise attacks on a variety of DeepFake benchmarks.

\textbf{Keywords:} DeepFakes, Blinking, Eye Aspect Ratio, Time Series Analysis, Convolutional Neural Networks, Machine Learning
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
First of all, I would like to thank my supervisor, Long Tran-Thanh, for his help in supervising me throughout the course of this project. It is thanks to him that the project is the success it is.

Secondly, thank you to Alia Meek for helping me keep sane throughout the course of the project and my third year as a whole.

Finally, I would like to thank my friends at Warwick. In particular, I would like to thank Serene Alrawi, Verity Anscombe, Oliver Cordeaux, Ethan Farrell, and many others for their help in keeping me motivated and allowing me to inflict my presentation on them multiple times.
\end{abstract}

\pagenumbering{roman}
\tableofcontents
\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}
\listofalgorithms
\addcontentsline{toc}{chapter}{List of Algorithms}
\listoftables
\addcontentsline{toc}{chapter}{List of Tables}
\newpage

%TC:endignore
\pagenumbering{arabic}
\input{dissertation/1introduction}
\input{dissertation/2litreview}
\input{dissertation/3design}
\input{dissertation/4evaluation}
\input{dissertation/5projectmanagement}
\input{dissertation/6conclusions}

\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography

%TC:ignore
\appendix
\input{dissertation/7appendix}
%TC:endignore

\end{document}